Phenotype and risk factors of venom-induced anaphylaxis: a case-control study of the European Anaphylaxis Registry

### 2020-05-27 analysis/paper/paper.Rmd
revision round 2

---
title: "Phenotype and risk factors of venom-induced anaphylaxis: a case-control study of the European Anaphylaxis Registry"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/the-journal-of-allergy-and-clinical-immunology.csl" # Insert path for the bib-style
---

@@

pacman::p_load("tidyvese")

@@

**Conclusion:** Regarding the fact that venom-induced anaphylaxis frequently affects the
cardiovascular system, patients were undertreated with epinephrine. The lack of skin
symptoms (i.e., urticaria or flushing) during anaphylaxis and baseline serum tryptase levels
within the upper normal limits were associated with severe reactions. Patients with serum
tryptase of above 8 ng/ml and a history of venom anaphylaxis may require additional
prophylaxis.

@@

Importantly, the absence of skin symptoms was associated with more severe VIA, which was still present after excluding patients with a known diagnosis of mastocytosis. Previous studies also observed this phenomenon [@Stoevesandt2012;@Fehr2019]. Subsequently, the correlation of BST levels with the severity of anaphylaxis lead us to identify an interaction between the absence of skin symptoms and VIA using generalized linearf regression.

@@

Based on our results, VIA is a distinctive phenotype of anaphylaxis, with a specific symptom profile and risk factors. VIA cases should undergo therapy according to the international management guidelines, and epinephrine should be given more often in VIA.

All cases should undergo appropriate allergologic testing and indication for SIT should be evaluated. Patients with BST above 8 ng/ml should undergo extensive diagnostic tests to exclude indolent systemic mastocytosis or MCAS and should be provided with two EAIs for acute self-management.

>>>>

---
title: "Phenotype and risk factors of venom-induced anaphylaxis: a case-control study of the European Anaphylaxis Registry"
output: 
    #bookdown::html_document2:
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: "references.bib"
csl: "../templates/the-journal-of-allergy-and-clinical-immunology.csl" # Insert path for the bib-style
---

@@

pacman::p_load("tidyverse")

@@

**Conclusion:** Using a large cohort of VIA cases, we have validated that patients 
with intermediate baseline serum tryptase levels (8 - 11 ng/ml) and without skin 
involvement have higher risk of severe VIA. Patients receiving beta-blockers or 
ACE-I had a higher risk of developing severe cardiovascular symptoms (including cardiac arrest) 
in VIA and non-VIA cases. Patients undergoing VIA received epinephrine less frequently than non-VIA cases.

@@

Importantly, the absence of skin symptoms was associated with more severe VIA, which was still present after excluding patients with a known diagnosis of mastocytosis (although in non-mastocytosis cases the difference between groups was small and the clinical relevance of this needs cautious evaluation). Previous studies also observed this phenomenon [@Stoevesandt2012;@Fehr2019]. Subsequently, the correlation of BST levels with the severity of anaphylaxis lead us to identify an interaction between the absence of skin symptoms and VIA using generalized linear regression.

@@

Based on our results, VIA is a distinctive phenotype of anaphylaxis, with a specific symptom profile and risk factors. Using a large cohort of VIA cases compared to a sex and age matched non-VIA cases, we have validated that patients with intermediate baseline serum tryptase levels (8 - 11 ng/ml) and without skin involvement have higher risk of severe VIA. Similarily, patients receiving beta-blockers or ACE-I had a higher risk of developing severe cardiovascular symptoms (including cardiac arrest) in VIA and non-VIA cases. Patients undergoing VIA received epinephrine less frequently than non-VIA cases.

VIA cases should undergo therapy according to the international management guidelines, and epinephrine should be given more often in VIA. All cases should undergo appropriate allergologic testing and indication for SIT should be evaluated along with patient education regarding the risk of future anaphylaxis. Patients with BST above 8 ng/ml should undergo extensive diagnostic tests to exclude indolent systemic mastocytosis or MCAS and should be provided with two EAIs for acute self-management.
